a and generators

### 2022-05-03 documentos/kraus.tex

Lindblad processes arise naturally in many theoretical~\cite{lindblad,kossa,kossa2,Gorini1976,cirac,davalosdivisibility} and
experimental~\cite{PhysRevA.67.042322} settings and are archetypical in decoherence dynamics. Moreover, these processes lead to a monotonically \afnote{monotonic (continuous)} lose of information~\cite{breuerreview} and describe non invertible channels in the asymptotic limit $t\to \infty$ (this can be seen from the monotonically \afnote{(continuous)} decreasing of the determinant, see Ref.~\cite{cirac}).
It is known that not every quantum channel can be seen as a snapshot of a
process
arising from a traditional Lindblad equation or even a time-dependent Lindblad
equation~\cite{cirac,davalosdivisibility}. 
Therefore, an interesting question is whether \pce{} channels can be seen as limit points of
some Markovian processes. In this section we prove what \afnote{that} in fact they are, and
give two examples of Markovian implementations.
%
The first
one consist in identifying each \pce{} channel as a fixed point of some pure
dissipative process. The second, in identifying each \pce{} channel as fixed
points of some memory-less collision model \afnote{The first of them consists in identifying each \pce{} channel as a fixed point of some pure dissipative process, and in the second implementation we relate each \pce{} channel to fixed
points of some memory-less collision model }.

>>>>

Lindblad processes arise naturally in many theoretical~\cite{lindblad,kossa,kossa2,Gorini1976,cirac,davalosdivisibility} and
experimental~\cite{PhysRevA.67.042322} settings and are archetypical in decoherence dynamics. Moreover, these processes lead to a monotonic (continuous) lose of information~\cite{breuerreview} and describe non invertible channels in the asymptotic limit $t\to \infty$ (this can be seen from the monotonically (continuous) decreasing of the determinant, see Ref.~\cite{cirac}).
It is known that not every quantum channel can be seen as a snapshot of a
process
arising from a traditional Lindblad equation or even a time-dependent Lindblad
equation~\cite{cirac,davalosdivisibility}. 
Therefore, an interesting question is whether \pce{} channels can be seen as limit points of
some Markovian processes. In this section we prove that in fact they are, and
give two examples of Markovian implementations.
%
The first of them consists in identifying each \pce{} channel as a fixed point of some pure dissipative process, and in the second implementation we relate each \pce{} channel to fixed
points of some memory-less collision model.
